TensorAlloy: a highly efficient atomistic neural network program for alloys

### 2019-04-26 doc/papers/nn/manuscript.tex
Version is CPC.v2. This manuscript has been submitted.

\title{
    TensorAlloy: a highly efficient atomistic neural network program for alloys
}
\author{Xin Chen}
\author{Xing-Yu Gao}
\author{Ya-Fan Zhao}
\author{De-Ye Lin}
\email{lindeye0716@163.com}
\author{Wei-Dong Chu}
\author{Hai-Feng Song}
\email{song\_haifeng@iapcm.ac.cn}
\affiliation{
    Institute of Applied Physics and Computational Math, 
    Beijing 100088, China}
\affiliation{
    CAEP Software Center for High Performance Numerical Simulation, 
    Beijing 100088, China}

\begin{abstract}
Atomistic modeling is important for studying physical and chemical properties of
materials. Recently, machine learning interaction potentials have gained much 
more attentions as they can provide density functional theory level predictions 
within negligible time. Currently, the symmetry function descriptor based 
atomistic neural network is the most widely used model for modeling alloys. 
To precisely describe complex potential energy surfaces, integrating advanced 
metrics, such as force or virial stress, into training can be of great help. 
However, the traditional way to construct a 
machine learning model computation graph starts from pre-computed descriptors, 
but not positions, due to technial challenges. Thus, deriving analytical atomic 
force and virial stress of a machine learning model becomes quite difficult as 
the partial derivations of descriptors with respect to positions need separate 
implementations, which requires plenty of efforts and its efficiency can not be 
guaranteed.
In this paper, we designed a new method, named the virtual atom approach, for 
implementing the symmetry function descriptor and the corresponding atomistic 
neural networks. With the virtual atom approach, we are able to build 
computation graph from atomic positions \textemdash but not descriptors 
\textemdash to total energy directly, thus asking modern machine learning 
platforms to compute atomic force and virial stress becoming possible. We also 
derived a simple and machine learning friendly equation for calculating virial 
stress. All these new algorithms have been implemented in our Python package, 
TensorAlloy. TensorAlloy supports constructing machine learning interaction 
potentials for both \textit{molecules} and \textit{solids} and one hour is 
sufficient for TensorAlloy to obtain models with state-of-art level accuracy.
\end{abstract}

>>>>

\title{
    TensorAlloy: a highly efficient atomistic neural network program for alloys
}
\author{Xin Chen}
\author{Xing-Yu Gao}
\author{Ya-Fan Zhao}
\author{De-Ye Lin}
\email{lindeye0716@163.com}
\author{Wei-Dong Chu}
\author{Hai-Feng Song}
\email{song\_haifeng@iapcm.ac.cn}
\affiliation{
    Institute of Applied Physics and Computational Mathematics, 
    Beijing 100088, China}
\affiliation{
    CAEP Software Center for High Performance Numerical Simulation, 
    Beijing 100088, China}

\begin{abstract}
Atomistic modeling is important for studying physical and chemical properties of
materials. Recently, machine learning interaction potentials have gained much 
more attentions as they can provide density functional theory level predictions 
within negligible time. Currently, the symmetry function descriptor based 
atomistic neural network is the most widely used model for modeling alloys. 
To precisely describe complex potential energy surfaces, integrating advanced 
metrics, such as force or virial stress, into training can be of great help. 
However, the traditional way to construct a 
machine learning model computation graph starts from pre-computed descriptors, 
but not positions, due to technical challenges. Thus, deriving analytical atomic 
force and virial stress of a machine learning model becomes quite difficult as 
the partial derivations of descriptors with respect to positions need separate 
implementations, which requires plenty of efforts and its efficiency can not be 
guaranteed.
In this paper, we designed a new method, named the virtual atom approach, for 
implementing the symmetry function descriptor and the corresponding atomistic 
neural networks. With the virtual atom approach, we are able to build 
computation graph from atomic positions \textemdash but not descriptors 
\textemdash to total energy directly, thus asking modern machine learning 
platforms to compute atomic force and virial stress becoming possible. We also 
derived a simple and machine learning friendly equation for calculating virial 
stress. All these new algorithms have been implemented in our Python package, 
TensorAlloy. TensorAlloy supports constructing machine learning interaction 
potentials for both \textit{molecules} and \textit{solids} and one hour is 
sufficient for TensorAlloy to obtain models with state-of-art level accuracy.
\end{abstract}
